---
title: "R&RStudioRefresher_Week1"
author: "AllysonSKelly"
date: "5/18/2020"
output:
  word_document: default
  html_document: default
---
#1  
```{r}
#install.packages(tidyverse)
library(tidyverse)
```

#2  
```{r}
diamonddata = diamonds
nrow(diamonddata)
```

#3  
```{r}
ggplot(diamonddata, aes(x = carat, y = price)) +geom_point()
```  
**as the carat increases, so does the price**

#4  
```{r}
ggplot(diamonddata, aes(x = carat, y = price, color = cut)) + geom_point()
```  
**as the carat and quality of cut increase, so does the price**  

#5  
```{r}
ggplot(diamonddata, aes(x = carat, y = price, color = cut)) + facet_wrap(~ color) + geom_point()
```  
**as the carat size, cut quality, and color quality increase, so does the price**  

#6  
```{r}
inventory <- read.csv(file.choose(), header = TRUE)
#inventory
#names(inventory)
```

#7  
```{r}
inventoryA <- inventory %>% filter(Supplier == "A")
#inventoryA
```  
**there are 3,695 rows in inventoryA.**  

#8  
```{r}
inventoryA = mutate(inventoryA, OnHandRatio = `On.Hand`/ `Annual.Demand`)
#inventoryA
```  
**it creates a new column containing the ratio of diamonds on hand to the annual demand**

#9
```{r}
avg_cost <- inventory %>% group_by(Item.SKU) %>% summarize(SKUAvgCost = mean(Cost.per.Unit....))
avg_cost
```

#10  
**I found the importing a file to be the most challenging. I have never utilized R or RStudtio before so there was a bit of external research I had to conduct on my own.**